RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-10-16 main.tex
:dizzy: Backscatter detection for SR

\begin{section}{Simulation Results}
	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision design for the RIScatter system in Fig. \ref{fi:riscatter_network}.
	We assume the AP-user distance is \qty{10}{\meter}, $K=2$ RIScatter nodes are randomly dropped within a disk of radius \qty{2}{\meter} centered at the user, the \gls{ap} is with $Q=4$ transmit antennas and an average power budget $P=\qty{36}{\dBm}$, the nodes employs \num{4}-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$, and the symbol period ratio is $N=20$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma
	\end{equation}
	together with a Rician fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at distance $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with entries of unit magnitude, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with entries in standard \gls{iid} \gls{cscg} distribution.
	We choose $\gamma_{\mathrm{D}}=2.6$, $\gamma_{\mathrm{F}}=2.4$, $\gamma_{\mathrm{B}}=2$, and $\kappa_{\mathrm{D}}=\kappa_{\mathrm{F}}=\kappa_{\mathrm{B}}=5$ for direct, forward and backward links.
	The finite threshold domain $\mathcal{T}$ comes from $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=9$ and $\varepsilon=\num{1e-3}$.
	All achievable rate curves/regions are averaged over \num{1000} realizations, and the parameters remain fixed unless otherwise specified.

@@

			In Fig. \ref{fi:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pgd} (on the first call within \gls{bcd}) and \gls{bcd} algorithms in each iteration.
			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations of closed-form expression \eqref{eq:input_kkt_solution} to converge to the \gls{kkt} input distribution.
			For $Q=4$, around \num{10} iterations are required for Algorithm \ref{al:active_beamforming} to converge, where the gradient needs to be evaluated by \eqref{eq:weighted_sum_mutual_information_gradient} and the step size needs to be refined by \gls{bls}.
			In comparison, the \gls{bcd} algorithm typically requires no more than \num{5} iterations to converge.
			At the following points (not shown here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
			Overall, we conclude the proposed algorithms are able to converge within moderate iterations and provide significant rate benefits for the RIScatter system.
		\end{subsubsection}
	\end{subsection}

@@

		For a fair comparison, we consider the setup in Fig. \ref{fi:riscatter_network} and employ \gls{ml} backscatter energy detection for these scattering applications:

@@

			which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k} \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.

@@

			\item \emph{\gls{sr}:} When $N$ is sufficiently large, the primary ergodic rate under semi-coherent detection can be approximated by \eqref{eq:primary_mutual_information} with uniform input distribution \cite{Long2020a}.
			When $s[n]$ is successfully decoded and the direct interference $\boldsymbol{h}_{\mathrm{D}}^H \boldsymbol{w} s[n]$ is perfectly cancelled, the intermediate signal used for backscatter detection is

@@

			By the law of large numbers, as $N$ goes to infinity, the \gls{pdf} of accumulated intermediate energy approaches
				f^{\text{\gls{sr}}}(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}})^{N-1} \exp \bigl(-(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}})/\sigma_v^2 \bigr)}{\sigma_v^{2N} (N-1)!},
				\label{eq:energy_distribution_sr}
			where $\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}} \triangleq N \bigl\lvert \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k} \boldsymbol{w} \bigr\rvert^2$. The \gls{ml} decision threshold is, $\forall l \in \mathcal{L} \setminus \{L\}$,
				t_l^{\text{\gls{sr}}} = \frac{\mu_{l-1}^{\text{\gls{sr}}} \exp \bigl((\mu_{l-1}^{\text{\gls{sr}}}-\mu_{l}^{\text{\gls{sr}}})/\sigma_v^2 (N-1)\bigr) - \mu_{l}^{\text{\gls{sr}}}}{\exp \bigl((\mu_{l-1}^{\text{\gls{sr}}}-\mu_{l}^{\text{\gls{sr}}})/\sigma_v^2 (N-1)\bigr) - 1}.
				\label{eq:detection_threshold_ml_sr}

>>>>

\begin{section}{Simulation Results}
	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision design for the RIScatter system in Fig. \ref{fi:riscatter_network}.
	We assume the AP-user distance is \qty{10}{\meter}, $K=2$ RIScatter nodes are randomly dropped within a disk of radius \qty{2}{\meter} centered at the user, the \gls{ap} is with $Q=4$ transmit antennas and an average power budget $P=\qty{36}{\dBm}$, the nodes employs \num{4}-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$, and the symbol period ratio is $N=20$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma,
	\end{equation}
	together with a Rician fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at distance $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with entries of unit magnitude, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with entries in standard \gls{iid} \gls{cscg} distribution.
	We choose $\gamma_{\mathrm{D}}=2.6$, $\gamma_{\mathrm{F}}=2.4$, $\gamma_{\mathrm{B}}=2$, and $\kappa_{\mathrm{D}}=\kappa_{\mathrm{F}}=\kappa_{\mathrm{B}}=5$ for direct, forward and backward links.
	The finite threshold domain $\mathcal{T}$ comes from $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=9$ and $\varepsilon=\num{1e-3}$.
	All achievable rate curves/regions are averaged over \num{1000} realizations, and the parameters remain fixed unless otherwise specified.

@@

			In Fig. \ref{fi:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates at $\rho=0$ for \gls{kkt}, \gls{pgd} (on the first call within \gls{bcd}) and \gls{bcd} algorithms in each iteration.
			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations of closed-form expression \eqref{eq:input_kkt_solution} to converge to the \gls{kkt} input distribution.
			For $Q=4$, around \num{10} iterations are required for Algorithm \ref{al:active_beamforming} to converge, where the gradient needs to be evaluated by \eqref{eq:weighted_sum_mutual_information_gradient} and the step size needs to be refined by \gls{bls}.
			In comparison, the \gls{bcd} algorithm typically requires no more than \num{5} iterations to converge.
			At the following points (not presented), the convergence of all three algorithms are much faster thanks to the progressive initialization.
			Overall, we conclude the proposed algorithms are able to converge within moderate iterations and provide significant rate benefits for the RIScatter system.
		\end{subsubsection}
	\end{subsection}

@@

		% TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
		% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
		% For a fair comparison, we consider the setup in Fig. \ref{fi:riscatter_network} and employ \gls{ml} backscatter energy detection for these scattering applications:
		For a fair comparison, we consider the setup in Fig. \ref{fi:riscatter_network} with \gls{ml} backscatter energy detection for these scattering applications (except \gls{sr}):

@@

			which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl((\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.

@@

			\item \emph{\gls{sr}:}\footnote{Existing } For a sufficiently large $N$, the primary ergodic rate under semi-coherent detection can be approximated by \eqref{eq:primary_mutual_information} with uniform input distribution \cite{Long2020a}.
			When $s[n]$ is successfully decoded and the direct interference $\boldsymbol{h}_{\mathrm{D}}^H \boldsymbol{w} s[n]$ is perfectly cancelled, the intermediate signal for backscatter detection is

@@

			Energy detection is generally suboptimal in this case
			% By the law of large numbers, for a very large $N$, the \gls{pdf} of accumulated intermediate energy approaches
			% 	f^{\text{\gls{sr}}}(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}})^{N-1} \exp \bigl(-(z-\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}})/\sigma_v^2 \bigr)}{\sigma_v^{2N} (N-1)!},
			% 	\label{eq:energy_distribution_sr}
			% where $\mu_{m_{\mathcal{K}}}^{\text{\gls{sr}}} \triangleq N \bigl\lvert \sum_{k} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k} \boldsymbol{w} \bigr\rvert^2$. The \gls{ml} decision threshold is, $\forall l \in \mathcal{L} \setminus \{L\}$,
			% 	t_l^{\text{\gls{sr}}} = \frac{\mu_{l-1}^{\text{\gls{sr}}} \exp \bigl((\mu_{l-1}^{\text{\gls{sr}}}-\mu_{l}^{\text{\gls{sr}}})/\sigma_v^2 (N-1)\bigr) - \mu_{l}^{\text{\gls{sr}}}}{\exp \bigl((\mu_{l-1}^{\text{\gls{sr}}}-\mu_{l}^{\text{\gls{sr}}})/\sigma_v^2 (N-1)\bigr) - 1}.
			% 	\label{eq:detection_threshold_ml_sr}
